Generalized Bradley-Terry models

### 2025-02-26 inst/jss_hyper3_real.Rnw
include a figure

Then, as before, we may define a profile likelihood function of $\lambda$:

<<calclikesushi, cache=TRUE>>=
f <- function(lambda){
   H <- make_sushi_H(lambda)
   maxp(H,give=1)$`Log-likelihood`
}
s <- exp(seq(from = log(0.9), to = log(10), len = 12))
L <- sapply(s,f)
@

<<plotsushi>>=
plot(log(s),L-max(L),type='b',xlab=expression(log(lambda)), ylab='Log-likelihood')
@

>>>>

Then, as before, we may define a profile likelihood function of
$\lambda$, Figure~\ref{profilesupportsushi}.

\begin{figure}[htbp]
  \begin{center}
<<calclikesushi, cache=TRUE>>=
f <- function(lambda){
   H <- make_sushi_H(lambda)
   maxp(H,give=1)$`Log-likelihood`
}
s <- exp(seq(from = log(0.9), to = log(10), len = 12))
L <- sapply(s,f)
plot(log(s),L-max(L),type='b',
     xlab=expression(log(lambda)), ylab='Log-likelihood')
@ 
\caption{A\label{profilesupportsushi} profile support function for the
  exchangeability term $\lambda$.  Vertical gray line shows
  $H_0\colon\lambda =1$, horizontal lines show the
  two-units-of-support limits}
\end{center}
\end{figure}
